%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

%\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\usepackage{url}

%\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Lebedev Mikhail} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

%----------------------------------------------------------------------------------------

\begin{resume}

\section{Personal information}
{\it Date of birth:} 01 December 1993 year. \\
{\it Place of birth:} Sudogda, Vladimir region, Russia. \\
{\it Languages:} Russian (native), English (B1). \\
{\it Family status:} single.

\section{Contact information:}
Saint-Petersburg \\
phone: +7 (925) 128 2306 \\
e-mail: \url{gloriouslair@gmail.com}

\section{Fields of interest:}
\begin{itemize}
\item Numerical Methods;
\item Data analysis;
\item Nonlinear dynamics;
\item Asymptotical analysis;
\item Machine Learning;
\item Bioinformatics.
\end{itemize}

\section{Education:}
{\it Bachelor degree:} 2010--2014, National Research University of Electronic Technology (MIET), Moscow, Zelenograd, Proezd 4806, building 5, 124498.

B.S. in Computer Engineering, G. L. Alfimov (advisor), \\
``Nonlinear modes in Bose-Einstein condensate model with periodically modulated nonlinearity''

Average diploma score: $4.95$.

{\it Master degree:} 2014--2016,  National Research University of Electronic Technology (MIET), Moscow, Zelenograd, Proezd 4806, building 5, 124498.

M.S. in Applied Mathematics, G. L. Alfimov (advisor) \\
``Solitons in nonlinear Schr\"odinger equation with periodically modulated nonlinearity''

Average diploma score: $ 4.93$.

\section{Online -- education}
{\it 1. Coursera.} Completed courses:
\begin{itemize}
\item Machine Learning (100\%);
\item Machine Learning Foundations: A Case Study Approach (92.0\%);
\item The Data Scientist’s Toolbox (94.7\%);
\item R Programming (100\%);
\item Getting and Cleaning Data (99\%);
\item Finding Hidden Messages in DNA (Bioinformatics I) (76.2\%);
\item Assembling Genomes and Sequencing Antibiotics (Bioinformatics II) (89.8\%);
\item Comparing Genes, Proteins, and Genomes (Bioinformatics III) (87.4\%).
\end{itemize}

{\it 2. Stepic.} Completed courses:
\begin{itemize}
\item Fundamentals of statistics (100\%)
\end{itemize}

\section{Competitions:}
\begin{itemize}
\item Regional Student Mathematical Competition of the North-West of Russia, 2013, 4th place in team standings;
\item 74th William Lowell Putnam Mathematical Competition, 2013 (Russian mirror), Diploma of the 3rd degree;
\item Vojt\v{e}ch Jarnic International Mathematical Competition, Ostrava, Czech Republic, 2013.
\end{itemize}

\section{Conferences, seminars, schools:}
\begin{itemize}
\item International Conference ``Hamiltonian Dynamics, Nonautonomous Systems and Patterns in PDEs''; Nizhni Novgorod, Russia, December 10-15, 2014.
\item Fundamental Mathematics and its Applications in the Natural Sciences; Ufa, Russia, September 27 -- October 1, 2015.
\item Scientific Seminar at the University of ITMO: ``Solitons in nonlinear-Schr\"odinger lattices'', St. Petersburg, Russia, February 4, 2016.
\item Summer School on Bioinformatics, July 20-25, 2015.
\item International Conference-School ``Dynamics, Bifurcations and Chaos''; Nizhni Novgorod, Russia, July 18-22, 2016.
\end{itemize}

\section{Employment:}
1. November, 2014 --- April, 2015: Alytics, Zelenograd, Moscow; \\ Programmer -- Mathematician / Junior.

2. October, 2015 --- June, 2016: Genotek, Moscow; Researcher.

3. June, 2017 --- {\it Nowadays}, : Genestack, Saint-Petersburg; Developer / Junior.

\section{Publications:}
1. G. L. Alfimov, M. E. Lebedev. On regular and singular solutions for the equation $u_{xx} + Q(x)u + P(x)u^3 = 0$ // Ufa Mathematical Journal, {\bf 7}, No. 2 (2015), 3--17. 

2. M. E. Lebedev, G. L. Alfimov, B. A. Malomed. Stable dipole solitons and soliton complexes in the nonlinear Schr\"odinger equation with periodically modulated nonlinearity // Chaos {\bf 26}, 073110 (2016).

\section{Skills:}
\begin{itemize}
\item C++, STL, Boost, MPI;
\item Python, NumPy, SciPy, Scikit-Learn, Pandas;
\item Statistical analysis with R;
\item Bash, Git;
\item MATLAB, MEX;
\item Numerical Methods;
\item Basics of Machine Learning;
\item Basics of Haskell;
\item LaTeX, Inkscape.
\end{itemize}

\section{Personal \\ interests:}
\begin{itemize}
\item Hiking, Kayaking;
\item Classical guitar, Сhoir singing.
\end{itemize}

\end{resume}
\end{document}